---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rrcompendiumDTB

<!-- badges: start -->
[![Travis-CI Build Status](https://travis-ci.com/annakrystalli/rrcompendiumDTB.svg?branch=master)](https://travis-ci.com/annakrystalli/rrcompendiumDTB)
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/annakrystalli/rrcompendiumDTB/master?urlpath=rstudio)
<!-- badges: end -->

This repository contains the data and code for our reproduction paper:

> Krystalli, A, (2018). _Partial Reproduction of Boettiger Ecology Letters 2018;21:1255–1267 with rrtools_.  <https://doi.org/{DOI-to-paper}>

Our reproduction pre-print is online here:

> Krystalli, A, (2018). _Partial Reproduction of Boettiger Ecology Letters 2018;21:1255–1267 with rrtools_, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/{DOI-to-compendium}>


### How to cite

Please cite this compendium as:

> Krystalli, A, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Partial Reproduction of Boettiger Ecology Letters 2018;21:1255–1267 with rrtools'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/{DOI-to-compendium}>

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/annakrystalli/rrcompendiumDTB/archive/master.zip>

Or you can install this compendium as an R package, rrcompendium, from GitHub with:


```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("annakrystalli/rrcompendiumDTB")
```


### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/) Copyright (c) 2018 Carl Boettiger.

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/), Copyright (c) 2018 Carl Boettiger.

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

